### 2015-05-27 writing/SNLI paper/corpus.tex
Misc updates.

For the premises, we used the Flickr30k corpus \cite{hodoshimage}, a database of approximately 160k captions  (corresponding to about 30k images) collected in an earlier crowdsourced effort. The captions were not authored by the photographers who took the source images, and they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \word{Our trip to the Olympic Peninsula}). We presented each caption to at least one worker, and some to more than one. With the exception of a handful that were flagged by workers as excessively difficult, our corpus contains at least three labeled pairs for each caption.

\noindent\todo{Explain our 5x->1x annotation switch...}

>>>>

For the premises, we used captions from the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions (corresponding to about 30k images) collected in an earlier crowdsourced effort. The captions were not authored by the photographers who took the source images, and they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \word{Our trip to the Olympic Peninsula}).
